Enhancement of SDR in Thessaloniki

### 2024-02-26 GHI_enh_04_investigate.tex
Commit 2024-02-26 12:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-02-22}

@@

@Zhang2018

@@

@@

\begin{verbatim}
2024-02-22 12:06:37.3 athan@tyler GHI_enh_04_investigate.R 0.439034 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-02-26}

@@

\hypertarget{zhang2018}{%
\subsection{@Zhang2018}\label{zhang2018}}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCEmonth-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climECEmonth-1} \end{center}

@@

\begin{verbatim}
2024-02-26 09:17:11.1 athan@tyler GHI_enh_04_investigate.R 0.584574 mins
\end{verbatim}
